Subject-specific curves for time series forecasting of smart meter demand

### 2020-04-03 sscts-paper-1-wp.Rmd
Removed level 4 numbering of sections

```{r accuracy-results}
accuracy_df %>%
  mutate_if(is.numeric, list(~ as.character(signif(., 3)))) %>%  # scientific notation for INS and decimals for all others
  group_by(working_hours) %>% 
  mutate_at(
    vars(mape, smape, mae, mase),
    ~ kableExtra::cell_spec(., format = "latex",
                            bold = if_else(. == min(.), T, F))
  ) %>%
  ungroup() %>% 
  select(
    Model = model, MAE = mae, MAPE = mape, sMAPE = smape,
    MASE = mase
  ) %>% 
  knitr::kable(
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,  # allows bold formatting to work
    caption = "(ref:accuracy-results)"
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::group_rows("All hours", 1, 8) %>%
  kableExtra::group_rows("Business hours", 9, 16) %>%
  kableExtra::group_rows("Non-business hours", 17, 24)
```

>>>>

```{r accuracy-results}
accuracy_df %>%
  mutate_if(is.numeric, list(~ as.character(signif(., 3)))) %>%  # scientific notation for INS and decimals for all others
  group_by(working_hours) %>%
  mutate_at(
    vars(mape, smape, mae, mase),
    ~ kableExtra::cell_spec(., format = "latex",
                            bold = if_else(. == min(.), T, F))
  ) %>%
  ungroup() %>%
  select(
    Model = model, MAE = mae, MAPE = mape, sMAPE = smape,
    MASE = mase
  ) %>%
  knitr::kable(
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,  # allows bold formatting to work
    caption = "(ref:accuracy-results)"
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::group_rows("All hours", 1, 8) %>%
  kableExtra::group_rows("Business hours", 9, 16) %>%
  kableExtra::group_rows("Non-business hours", 17, 24)
```
